A Statically Checked Interface and a Checker for Tezos Smart Contracts

### 2024-06-20 reports/2024-06-30/report.tex
draft report

\section{Progress Report July 2023 - December 2023}
\label{sec:executive-summary}

@@

Currently, the project is slightly delayed but making good progress. Ms.\ Doan
returned from  maternal leave in October 2023.

@@

\begin{itemize}
\item Activity: Development of a dynamic logic as a formal foundation for symbolic interpretation of Michelson. \\
  $\Rightarrow$ This activity progressed significantly.  The master's
  thesis has been completed in November and is currently under review (by the examiner).
\item Deliverable: Formalization (in Agda) of a dynamic logic for a core fragment of Michelson with soundness proof. \\
  $\Rightarrow$ This deliverable is available  at
  \url{https://github.com/Barnaboss/thesis-michelsonDL}. It will be
  released after the thesis review period.
\item Deliverable: Paper about this formalization (writeup starting
  July 2023). \\
  $\Rightarrow$ The paper will be based on the master's thesis, so the final writing
  starts after completion of the thesis review. The goal is to submit to a
  conference during spring.
\end{itemize}

@@

\begin{itemize}
\item Activity: Implementation of symbolic interpreter for a core
  fragment of Michelson in OCaml based on the SMT solver Z3. \\
  $\Rightarrow$ This activity has been driven by Doan between January and June
  2023 and then further after her return from maternity leave. 
\item Deliverable: Symbolic interpreter. \\
  $\Rightarrow$ The current prototype of the symbolic interpreter is available here
  \url{https://github.com/proglang/tezos-project/tree/master/static_checker}
\item Deliverable: Doan completed two case studies with example contracts.
\item Deliverable: Paper or tutorial on this tool (writeup started,
  submission planned for a deadline in spring) \\
  $\Rightarrow$ A draft is available here \url{https://github.com/proglang/tezos-project/tree/master/symbolic-execution/paper}
\end{itemize}

>>>>

\section{Progress Report January 2024 - June 2024}
\label{sec:executive-summary}

@@

Currently, the project is still behind schedule, but making good
progress after Ms.\ Doan's return from  maternal leave in October 2023.

@@

\begin{itemize}
\item Activity: Development of a dynamic logic as a formal foundation for symbolic interpretation of Michelson. \\
  $\Rightarrow$  The master's thesis has been completed in November and grading is complete.
\item Deliverable: Formalization (in Agda) of a dynamic logic for a core fragment of Michelson with soundness proof. \\
  $\Rightarrow$ This deliverable is available  at
  \url{https://github.com/Tezos-Project-Uni-Freiburg/michelson-dynamic-logic}. It will be
  released as an artifact at the time the paper is published.
\item Deliverable: Paper about this formalization (writeup starting
  July 2023). \\
  $\Rightarrow$ The paper is based on the master's thesis. The Agda code
  from the thesis as well as the text had to undergo significant
  revision. The paper was submitted to ECOOP on April 18 and has been
  conditionally accepted. The revision is due July 7.
\end{itemize}

@@

\begin{itemize}
\item Activity: Implementation of symbolic interpreter for a core
  fragment of Michelson in OCaml based on the SMT solver Z3. \\
  $\Rightarrow$ This activity has been driven by Doan between January and June
  2023 and then further after her return from maternity leave. 
\item Deliverable: Symbolic interpreter. \\
  $\Rightarrow$ The current prototype of the symbolic interpreter is available here
  \url{https://github.com/proglang/tezos-project/tree/master/static_checker}
\item Deliverable: Doan completed two case studies with example contracts.
\item Deliverable: Paper or tutorial on this tool (writeup finished,
  first submission January 18, second submission May 31) \\
  $\Rightarrow$ Current submission is available here \url{https://github.com/proglang/tezos-project/tree/master/symbolic-execution/paper}
\end{itemize}
